%-------------------------
% Resume in Latex
% Customized for Shravan Ramakunja
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\usepackage[T1]{fontenc}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\renewcommand*\familydefault{\sfdefault}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey}{\titlerule[2pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey}\small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2}\\
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

\begin{center}
    \textbf{\Huge Shravan Ramakunja} \\ \vspace{5pt}
    \small \faEnvelope \hspace{2pt} \texttt{shravanramakunja@gmail.com} \hspace{2pt} $|$
    \hspace{2pt} \faGithub \hspace{2pt} \href{https://github.com/shravanramakunja}{\myuline {github.com/shravanramakunja}} \hspace{2pt} $|$
    \hspace{2pt} \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/shravan-ramakunja-4b3a25291/}{\myuline {linkedin.com/in/shravan-ramakunja-4b3a25291}} \hspace{2pt} $|$
    \hspace{2pt} \faGlobe \hspace{2pt} \href{https://www.shravanramakunja.in/}{\myuline {shravanramakunja.in}}
    \\ \vspace{-3pt}
\end{center}

\section{SUMMARY}
\resumeSubHeadingListStart
  \item\small{
    Engineering student focused on AI applications, backend systems, and practical full-stack product development.
  }
\resumeSubHeadingListEnd

\section{EXPERIENCE}
\resumeSubHeadingListStart
  \resumeSubheading
    {Nova Innovative Compskey (NIC)}{2025 -- Present}
    {President}{India}
    \resumeItemListStart
      \resumeItem{Leading innovation initiatives, student collaboration, and project execution across engineering teams.}
    \resumeItemListEnd

  \resumeSubheading
    {Nova Innovative Compskey (NIC)}{Nov. 2024 -- Present}
    {Design Sub Lead}{India}
    \resumeItemListStart
      \resumeItem{Guiding design direction for engineering projects and coordinating with development contributors.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading
    {MVJ College of Engineering}{2023 -- Present}
    {B.E. in Engineering}{Bengaluru, India}
\resumeSubHeadingListEnd

\section{PROJECTS}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{SwitchBoard} $|$ \href{https://swtich-board.vercel.app/}{\myuline {Live Project}}}{Current}
    \resumeItemListStart
      \resumeItem{Built a full-stack school attendance platform for daily tracking, student records, and reporting workflows.}
      \resumeItem{Implemented role-based interfaces for staff and administrators to reduce manual follow-up.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{AutoBulkSender} $|$ \href{https://github.com/shravanramakunja/AutoBulkSender}{\myuline {GitHub}}}{2026}
    \resumeItemListStart
      \resumeItem{Automated certificate generation and bulk email delivery from spreadsheet-based participant data.}
      \resumeItem{Reduced manual effort for event teams by creating a reusable end-to-end workflow.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{EventEase} $|$ \href{https://github.com/shravanramakunja/EventEase}{\myuline {GitHub}}}{2026}
    \resumeItemListStart
      \resumeItem{Developed an event registration and check-in platform with automated attendance workflows.}
      \resumeItem{Centralized registration, check-in, and participant updates to improve organizer operations.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Inquisit} $|$ \href{https://github.com/shravanramakunja/Inquisit}{\myuline {GitHub}}}{2026}
    \resumeItemListStart
      \resumeItem{Built a RAG application for document-grounded question generation and answer evaluation.}
      \resumeItem{Implemented retrieval + generation pipeline to improve relevance and reduce hallucinations.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{CodeSage} $|$ \href{https://github.com/shravanramakunja/CodeSage}{\myuline {GitHub}}}{2026}
    \resumeItemListStart
      \resumeItem{Built an AI-assisted review workflow that generates pull request feedback and speeds up review cycles.}
      \resumeItem{Produced actionable comments to improve code quality and maintain developer velocity.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
    \textbf{Core} {: React, Python, Node.js, MongoDB, Agentic Systems, Backend Development} \\
    \textbf{Links} {: \href{https://github.com/shravanramakunja}{\myuline {GitHub}}, \href{https://www.linkedin.com/in/shravan-ramakunja-4b3a25291/}{\myuline {LinkedIn}}, \href{https://www.shravanramakunja.in/}{\myuline {Portfolio}}}
  }}
\end{itemize}

\end{document}
